{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-07 documents/acknowledgement.tex
"Prompt" electroporation
scd5000 import?
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Acknowledgements}\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Yuriy S at Indiana, and Prof. Sarris at UofT.

@@

Sandra at the Resources Sharing Department at YorkU for spending an hour looking for the Gray paper.

@@

Thanks to L.H. for wisdom regarding this project, and to my friend Eric and friends at SimCoLab.

>>>>

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Yuriy S at Indiana, and Prof. Sarris at UofT. Sean Hum and [that other guy?] from UofT.

@@

Sandra and colleagues at the Resources Sharing Department at YorkU for spending an hour looking for 
the Gray paper.

@@

Thanks to L.H. for wisdom regarding this project, and to my friend Eric, and friends at SimCoLab.

### 2021-01-07 documents/background.tex
Minimization
VMD signal library
scd5000 import?
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

@@

>>>>

Unfortunately, this cannot be an exhaustive list. 20,000 papers.

significant work on elecroporation for cancer, water treatment, and food sterilization.

can we bind a highly-charged something-or-other to the virus?
or a little magnetite crystal - like that magnetoacoustic paper?

@@

\subsection{Liburdy's oxidation-dependent lipid leakage}

\subsection{Tsen femtosecond laser ISRU}

Impulsive stimulated Raman scattering. We confess to not having studied these mechanisms in great detail. Does not directly act on 
the vibrational mode; the optimal pulse duration is some fraction of the period of the mode in question.
 Unfortunately, these results appear to have failed replication \cite{No2011}. In any case, inactivation requires a very long duration; 
 unlikely to be of great clinical use.

Ultrafast femtosecond laser pulses

\subsection{Free-electron-laser }

### 2021-01-07 documents/brillouin_pulse_math.tex
liposome
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

@@

Are similar to soliton

@@

\footnotetext{Some of the initial work on these precursors (or "forerunners", as they were known at the time) apparently neglected some of the higher-order terms, leading to the conclusion that the signals were "very weak". However, the amplitude is often much greater than that of the carrier. See wikipedia.}

These are fascinating structures which arise as a result of two aspects Albanese \cite{Shortrisetime1989}:

The highly dispersive nature of tissue, which

The change in loss - and increase in penetration depth -

A third aspect leads to the formation of the prototypical brilluoin precursor: any "sharp" beginning or end of a wave, or other spatially confined structure, includes harmonics up to these \footnotemark

@@

At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the brilluoin train drives the virus with an equally, implementing this would decrease the field at the skin required for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).

@@

@@

 Unfortunately, despite NLTLs producing strong wideband components, they do not appear to satisfy the requirements for Brillouin pulses. 
\begin{autem}
	This should be replicated.
\end{autem}

@@

\begin{toolchain}
An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic complex permittivity. It then drives a
damped harmonic oscillator that is initially at rest.\\

@@

\section{Zhu et al 's dispersive waveform optimization propagation formulation}

The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, This is based on a lagrange multiplier technique\cite{Methods1989} and variational calculus\footnotetext .

@@

Neither Mathematica's VariationalD, Matlab's Fundiff, nor Maple's functionalDerivative seem to yield any meaningful result for grad xi.\\

@@

Aha! That's the ticket!

@@

Numerically solving optimal control problems using CG was noted by Lasdon \cite{conjugate1967} and revisited by Kek \cite{Conjugate}.

>>>>

\section{The Brillouin precursors}

@@

@@

These are fascinating structures which arise as a result of two aspects (Albanese 
\cite{Shortrisetime1989}):

The highly dispersive nature of tissue, which causes a peculiar distortion of short pulses,

The change in loss (the complex part of the permittivity, or the) and increase in penetration depth 
-

A third aspect leads to the formation of the prototypical brilluoin precursor: any "sharp" 
beginning or end of a tone, or other spatially confined structure in a waveform, includes harmonics 
up to these \footnotemark

@@

At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the Brillouin train 
drives the virus with an equally, implementing this would decrease the field at the skin required 
for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than 
an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).

@@

Also another really good paper that I can't find.

@@

Unfortunately, despite NLTLs producing strong wideband components, in cursory simulations they do 
not appear to satisfy the requirements for Brillouin pulses. Our working hypothesis is that this is 
because of destructive interference from the falling edge that immediately follows; but this is 
mere speculation.
\begin{autem}
	This should be replicated.
\end{autem}

@@

\begin{toolchain}
An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic complex 
permittivity.

It then drives a damped harmonic oscillator that is initially at rest.\\

@@

\printendnotes

\subsubsection{Zhu et al 's dispersive waveform optimization propagation formulation}

The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, 
Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, 
This is based on a lagrange multiplier technique\cite{Methods1989} and variational 
calculus\footnotetext{} .

@@

Neither Maxima, SageMath, Mathematica's VariationalD, Matlab's Fundiff, nor Maple's 
functionalDerivative seem to yield any meaningful result for grad xi.\\

@@

@@

Numerically solving optimal control problems using CG was noted by Lasdon \cite{conjugate1967} and 
revisited by Kek \cite{Conjugate}. They reduce the computational workload by first computing the 
gradient function by hand.

### 2021-01-07 documents/paper.tex
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

\subfile{introduction}

@@

@@

\clearpage
\printbibliography[heading=none, title={}, keyword={Flagship}]
\printbibliography[heading=none, title={}, keyword={standards}]

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{1}
{\Large The Experiment}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{\textbf{Centrifugal microfluidics}}\

The field of centrifugal microfluidics is accelerating.

Many CD microfluidics systems use standard CD molding techniques for the channels and machining techniques, using either acrylic or silicone. The turbidity sensor is most sensitive if the plastic is clear. Sterilization does not seem to be discussed.

Polypropylene is the ideal material, being almost indefinitely autoclavable. It is quite difficult to machine.

@@

\subfile{acknowledgement}

@@

\printbibliography[ title={All references}]

>>>>

%\subfile{introduction}

@@

\subfile{background}

@@

\clearpage
%\printbibliography[heading=none, title={}, keyword={Flagship}]
\printbibliography[heading=none, title={}, keyword={standards}]

@@

@@

%\subfile{acknowledgement}

@@

%\printbibliography[]
%\printbibliography[title={All references}]

### 2021-01-07 documents/supplemental.tex
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\Huge Captain's Log, Supplemental}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{quote}
The accumulated insight of a [] worker frequently merits recording when no documentation can be given.
\end{quote}

- W. G. Cochran et al, \cite{Statistical1953}

many of the base facts - and some of the most useful and simplest methods - are in the early 
papers, and later papers generally just refer to the previous ones. it can be of some use to try to 
find the earliest papers. For instance, when searching for methods for the bacteriophage, lots of 
modern detail-scarce papers appear, but none of the most important Delbruck papers.

"when searching for old papers, use the terminology of the day. millimicrosecond, for instance, for 
nanosecond".

@@

\begin{quote} 
Similarly, IEEE-ICES urges the Commission to adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g. [snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW. We decline to increase the 1-mW threshold.".

@@

\printbibliography[heading=none, title={}, keyword={amplifier}]

@@

\printbibliography[heading=none, title={}, keyword={rectifier}]

>>>>

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\Huge Captain's Log, Supplemental}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{fquote}[Paraphrased from W. G. Cochran][\cite{Statistical1953}]
The accumulated insight of a worker frequently merits recording when no documentation can be given.
\end{fquote}

Materials

polycarbonate

infinitely autoclaveable. However, clear has possible issues with flurosescence background. white 
is 
generally recommended for fluro.

polypropylene
autoclaveable, although softening causes warping if not supported. Difficult form strong bonds to 
with adhesives. causes "hairs" when machining.

There is some good advice in the Government Accountability one is especially sage:

"Be as quantitative as possible."

source of truth in the home lab. For instance, you can build an oscilloscope, or a pulse generator, 
but not both.

\subsubsection{Old papers}

many of the base facts - and some of the most useful and simplest methods - are in the early 
papers, and later papers generally just refer to the previous ones. it can be of some use to try to 
find the earliest papers.

For instance, when searching for methods for the bacteriophage, lots of modern detail-scarce papers 
appear, but none of the most important Delbruck papers. Books are one way to side-step this issues

When searching for old papers, use the terminology of the day. millimicrosecond, for instance, for 
nanosecond".

find government gray-literature publications on the topic. They are often

find research groups with "lists of publications".

\subsubsection{Cargo-cult}

@@

Similarly, IEEE-ICES urges the Commission to adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g. [snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW. We decline to increase the 1-mW threshold.".

@@

%\printbibliography[heading=none, title={}, keyword={amplifier}]

@@

%\printbibliography[heading=none, title={}, keyword={rectifier}]
